### 2021-04-13 paper/ase21/intro.tex
[ASE21] Till 4.2
[ASE21] Added todos
[ASE21] link of ECMA262 discussion in intro

Unfortunately, there is no existing tool to automatically detect bugs in the
rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
have tried to resolve this problem using additional annotations in abstract
algorithms.  Additional annotations make the specification more readable and
also they are useful for the specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, static analyzers~\cite{safe, tajs,
jsai, wala}, and verification tools~\cite{javert}.  Thus, they decided to
manually insert two different annotations: 1) \textit{assertions} to denotes the
assumptions in a certain point of abstract algorithms, and 2) two different
\textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
records might be abrupt or not.  For example, ``Assert: Type(\textit{O}) is
Object'' denotes that the variable $\textit{O}$ always has an Object value at
this point and ``? \textbf{GetV}(\textit{V}, \textit{P})'' denotes that return
values of \textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions.
Moreover, they recently started the internal discussion of manual type
annotations for variables, parameters, and return values for each abstract
algorithm.  However, to manually annotate types for all of them without any
automated tool is also labor-intensive and error-prone.  Furthermore, even
though the such manual type annotations can give more information for manual
checking of specification updates, it still does not provide any automatic
approach to detect specification bugs.

>>>>

% TODO: links in footnote
Unfortunately, there is no existing tool to automatically detect bugs in the
rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
have tried to resolve this problem using additional annotations in abstract
algorithms.  Additional annotations make the specification more readable and
also they are useful for the specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, static analyzers~\cite{safe, tajs,
jsai, wala}, and verification tools~\cite{javert}.  Thus, they decided to
manually insert two different annotations: 1) \textit{assertions} to denotes the
assumptions in a certain point of abstract algorithms, and 2) two different
\textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
records might be abrupt or not.  For example, ``Assert: Type(\textit{O}) is
Object'' denotes that the variable $\textit{O}$ always has an Object value at
this point and ``? \textbf{GetV}(\textit{V}, \textit{P})'' denotes that return
values of \textbf{GetV}(\textit{V}, \textit{P}) might be abrupt completions.
Moreover, they recently started the internal discussion of manual type
annotations for variables, parameters, and return values for each abstract
algorithm~\footnote{https://github.com/tc39/ecma262/pull/545\#issuecomment-559292107}.
However, to manually annotate types for all of them without any automated tool
is also labor-intensive and error-prone.  Furthermore, even though the such
manual type annotations can give more information for manual checking of
specification updates, it still does not provide any automatic approach to
detect specification bugs.
